\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
updated

%\begin{figure}[ht]
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
%\label{fig:fem_cv}
%\end{figure}

%\begin{figure}[ht]
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

%%%%
%%%%  FIGURE 1
%%%%
\begin{figure}[ht]
\centering
\vbox{\includegraphics[width=\textwidth]{./Pics/phase_vol_frac_uni_perm_1}}
\caption{Schematics of flow instabilities during injection of a pure low viscosity fluid (left-hand side in red) into a domain saturated with a second fluid (dark blue). The ratio of viscosity between the two fluids is 5. In this case, the initially piston shape front collapses leading to the formation of several fingers.}
\label{fig:simple_case}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE 2
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/P1DGP2}}
\hbox{\hspace{6cm}(a)}
\vspace{.5cm}
\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/element_n}}
\hbox{\hspace{6cm}(b)}}
\caption{Sketches of FE-pairs: (a) 2D representation of the \PN[1]{2} element-pair used in this work. Shaded areas denote control volumes (in which scalar fields such as phase saturation, temperature, density etc are stored); blue and white circles represent pressure and velocity nodes, respectively. (b) Simplified representation of field storage in a \PN[1]{1} element-pair: permeability $\left(K_{i}\right)$ and porosity $\left(\phi_{i}\right)$ are stored in $P_{0}DG$ space ($A$), whereas all other scalar fields (e.g., saturation, density, viscosity, relative permeability etc) are stored in CV space ($B$). \red{(KOSTAS, COULD YOU: (a) REPLACE 1 BY i (top quad of ELEMENT B) AND (b) REMOVE THE WHITE CIRCLES IN ELEMENT A)}.}
\label{fig:fem_cv}
\end{figure}

%%%%
%%%%  FIGURE 3
%%%%
\begin{figure}[ht]
\vbox{
\hbox{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2}}
\vspace{-0.cm}
\hbox{\hspace{5cm}(a)}
\vspace{-0.cm}
\hbox{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot}}
\vspace{-0.cm}
\hbox{\hspace{5cm}(b)}
}\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region. The mesh is unstructured and fixed with 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}\label{fig:square}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%
%%% Figure 1 %%%
%%%%%%%%%%%%%%%%
\begin{figure}[h]
   \begin{center}
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
\label{fig:fem_cv}
\end{center}
\end{figure}

\clearpage
%%%%%%%%%%%%%%%%
%%% Figure 2 %%%
%%%%%%%%%%%%%%%%
\begin{figure}[h] 
   \begin{center}
\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements. The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
\label{fig:fem_elem}
\end{center}
\end{figure}

\clearpage

%%%%
%%%%  FIGURE 1
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue). The ratio of viscosity between the two fluids is 5. In this case, the initially piston shape front collapses leading to the formation of several fingers.}
\label{fig:simple_case}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
\label{fig:fem_cv}
\end{figure}

%\begin{figure}[h] 
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
%\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
%\label{fig:fem_elem}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
\label{fig:fem_elem}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{6.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}
